Summary

### 2015-05-10 inst/examples/summary.Rmd
limits fix (cheap)

```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
ntop <- 50
a <- rev(rev(sort(table(paste(df$author_family,df$author_first,sep=", "))))[1:ntop])
par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
```

>>>>

```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
df$author <- paste(df$family_name,df$first_name,sep=", ")
ntop <- 50
a <- rev(rev(sort(table(df$author)))[2:ntop+1])
par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
```
